Exceedance probability comparison for the simplified Naomi model

### 2023-12-28 src/naomi-simple_exceedance/exceedance.Rmd
Make the exceedance plots difference on the y-axis

exceedance_manuscript_plot_second90 <- df_wide %>%
  filter(indicator == "Second 90") %>%
  pivot_longer(cols = c("GEB", "GPCA-AGHQ"), names_to = "method", values_to = "estimate") %>%
  ggplot(aes(x = NUTS, y = estimate)) +
    geom_point(aes(col = sex), shape = 1, alpha = 0.4) +
    coord_fixed(ratio = 1) +
    scale_colour_manual(values = c("#0072B2", "black"), labels = c("Female", "Male")) +
    geom_abline(slope = 0, intercept = 0, linetype = "dashed", col = "#E69F00") +
    geom_text(
    data = df_metrics %>%
        filter(indicator == "Second 90"),
      aes(x = -Inf, y = Inf, label = label),
      size = 3, hjust = 0, vjust = 1.5
    ) +
    facet_grid(indicator ~ method) +
    labs(x = "NUTS", y = "Absolute difference to NUTS", col = "Sex") +
    theme_minimal()

@@

exceedance_manuscript_plot_1inc <- df_wide %>%
  filter(indicator == "High incidence") %>%
  pivot_longer(cols = c("GEB", "GPCA-AGHQ"), names_to = "method", values_to = "estimate") %>%
  ggplot(aes(x = NUTS, y = estimate)) +
    geom_point(aes(col = sex), shape = 1, alpha = 0.6) +
    coord_fixed(ratio = 1) +
    scale_colour_manual(values = c("#0072B2", "black"), labels = c("Female", "Male")) +
    geom_abline(slope = 0, intercept = 0, linetype = "dashed", col = "#E69F00") +
    geom_text(
      data = df_metrics %>%
        filter(indicator == "High incidence"),
      aes(x = -Inf, y = Inf, label = label),
      size = 3, hjust = 0, vjust = 1.5
    ) +
    facet_grid(indicator ~ method) +
    labs(x = "NUTS", y = "Absolute difference to NUTS", col = "Sex") +
    theme_minimal()

>>>>

exceedance_manuscript_plot_second90 <- df_wide %>%
  filter(indicator == "Second 90") %>%
  pivot_longer(cols = c("GEB", "GPCA-AGHQ"), names_to = "method", values_to = "estimate") %>%
  ggplot(aes(x = NUTS, y = estimate - NUTS)) +
    geom_point(aes(col = sex), shape = 1, alpha = 0.4) +
    scale_colour_manual(values = c("#0072B2", "black"), labels = c("Female", "Male")) +
    geom_abline(slope = 0, intercept = 0, linetype = "dashed", col = "#E69F00") +
    geom_text(
    data = df_metrics %>%
        filter(indicator == "Second 90"),
      aes(x = -Inf, y = Inf, label = label),
      size = 3, hjust = 0, vjust = 1.5
    ) +
    facet_grid(indicator ~ method) +
    labs(x = "Estimate", y = "Absolute difference to NUTS", col = "Sex") +
    theme_minimal()

@@

exceedance_manuscript_plot_1inc <- df_wide %>%
  filter(indicator == "High incidence") %>%
  pivot_longer(cols = c("GEB", "GPCA-AGHQ"), names_to = "method", values_to = "estimate") %>%
  ggplot(aes(x = NUTS, y = estimate - NUTS)) +
    geom_point(aes(col = sex), shape = 1, alpha = 0.6) +
    scale_colour_manual(values = c("#0072B2", "black"), labels = c("Female", "Male")) +
    geom_abline(slope = 0, intercept = 0, linetype = "dashed", col = "#E69F00") +
    geom_text(
      data = df_metrics %>%
        filter(indicator == "High incidence"),
      aes(x = -Inf, y = Inf, label = label),
      size = 3, hjust = 0, vjust = 1.5
    ) +
    facet_grid(indicator ~ method) +
    labs(x = "Estimate", y = "Absolute difference to NUTS", col = "Sex") +
    theme_minimal()
